Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-08-25 draftfinalreport_v4.Rnw
update silly table that didn't work with latex()

\begin{table}[hbtp] \tiny
\captionsetup{width=1\textwidth, font={footnotesize}}
<<results=tex,echo=FALSE>>=
colnames(PerCap)<-c("NZDep","Age","Ethnicity","Population","Cases","Per capita")
latex(PerCap, file="", table.env=FALSE,rowname=NULL)
@
\caption{Measles cases (Cases), population sizes (Population) and per capita rates per 10,000 (Per capita) of measles in specific age (Age), ethnicity (Ethnicity) and socio-economic deprivation (NZDep) categories from 2007-2014. MELAA is Middle Eastern/Latin American/African.}
\label{table:percap}
\end{table}

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE TABLE %%%%%%%%%%%%%%%%%%%%%%
%%%% find out why 'Cases' col name appears as 'Cases 1' %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% check if \tiny means the page # is outside the table %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{table}[hbtp] \tiny
\centering
\captionsetup{width=1\textwidth, font={footnotesize}}
<<results=tex,echo=FALSE>>=
colnames(PerCap)<-c("NZDep","Age","Ethnicity","Population","Cases","Per capita")
print(xtable(PerCap), include.rownames=FALSE, floating=FALSE)
@
\caption{Measles cases (Cases), population sizes (Population) and per capita rates per 10,000 (Per capita) of measles in specific age (Age), ethnicity (Ethnicity) and socio-economic deprivation (NZDep) categories from 2007-2014. MELAA is Middle Eastern/Latin American/African.}
\label{table:percap}
\end{table}
